Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-21 Paper/Manuscript.tex
Small changes to text

In this implementation (ref code) several choices have been made. Some of these are well founded in signal processing literature whereas others are of a more practical and ad-hoc nature, where other approaches could been equally valid. These include, as examples,\\ 
Transmit pulse\\
Tapering of the transmit pulse\\
Decimation factors and filters\\
When Convoling the recieved signal with the transmit pulse - edge cases\\
Assuemd four sector transducer\\
Matched load - hvor stor effekt å gå utover \\
Assumed an impedance (trancuder)\\
Effective pulse duration...\\
Assuming SED algorithm, know the target depth. Improvements possible (SED for broadband). Number of samples for pulse comp - what is included, dense aggregations, sidelobes - pc, ...\\
Window size\\
Edge cases - removed\\

>>>>

In this implementation (ref code) several choices have been made. Some of these are well founded in signal processing literature whereas others are of a more practical and ad-hoc nature, where other approaches could been equally valid. These include, as examples,\\ 
How to handle calibration, interpolation, missing calibration\\
Transmit pulse\\
Tapering of the transmit pulse\\
Decimation factors and filters\\
When Convoling the recieved signal with the transmit pulse - edge cases\\
Assuemd four sector transducer\\
Matched load - hvor stor effekt å gå utover \\
Assumed an impedance (trancuder)\\
Effective pulse duration...\\
Assuming SED algorithm, know the target depth. Improvements possible (SED for broadband). Number of samples for pulse comp - what is included, dense aggregations, sidelobes - pc, ...\\
Window size\\
Edge cases - removed\\
